Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-16 doc/journal/fpgapaperfinal/FPGAPaper/partitioning.tex
Updating reference for packing constraints
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4547 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

We refer to this type of per-block set of constraints as heterogeneous balance constraints. Note that there are complex legality constraints governing which LUTs and FFs can be packed into legal logic blocks, as well as which multipliers can be packed into legal DSP blocks [ref AAPack]. As the partitioner is not aware of these constraints, flow 3 above (which runs the partitioner after function block packing) will be able to more precisely balance resource use across partitions.

>>>>

We refer to this type of per-block set of constraints as heterogeneous balance constraints. Note that there are complex legality constraints governing which LUTs and FFs can be packed into legal logic blocks, as well as which multipliers can be packed into legal DSP blocks~\cite{luu2014vtr}. As the partitioner is not aware of these constraints, flow 3 above (which runs the partitioner after function block packing) will be able to more precisely balance resource use across partitions.
